### 2020-06-03 5_evaluation.tex
Fiddle with wording to save space.

Our MPI+CUDA implementation uses an offload model with data copied to and from the GPU on each step. We test
two configurations: \lstinline{w1} uses 1 task per GPU, whereas
\lstinline{w4} overdecomposes, using 4 MPI
ranks per GPU to push work to the GPU in parallel.
\lstinline{w4} achieves higher FLOP/s but
drops more rapidly at small problem sizes, due to the overhead of
scheduling $4\times$ as many CUDA kernel launches. Either way,
GPUs require more work to achieve high performance, and the overhead
of copying data dominates at small task
granularities, where CPUs achieve higher
performance. While Figure~\ref{fig:cuda-efficiency} is not couched in
terms of METG (as peak performance on CPU and GPU are very
different), the conclusion here is similar to
Section~\ref{subsec:scalability}: the cost of sending data and
tasks to the GPU imposes a floor on task granularity relative to the CPU, reducing the advantage at small task granularities of
very lightweight mechanisms such as those in MPI.

>>>>

Our MPI+CUDA code uses an offload model with data copied to/from the GPU every step. In our tests, \lstinline{w1} uses 1 task per GPU, whereas
\lstinline{w4} overdecomposes, using 4 MPI
ranks per GPU to push work to the GPU in parallel.
\lstinline{w4} achieves higher FLOP/s but
drops more rapidly at small problem sizes, due to the overhead of
running $4\times$ as many CUDA kernels. Either way,
GPUs require more work to achieve high performance, and the overhead
of copying data dominates at small task
granularities, where CPUs achieve higher
performance. While Figure~\ref{fig:cuda-efficiency} is not couched in
terms of METG (as peak performance on CPU and GPU are very
different), the conclusion here is similar to
Section~\ref{subsec:scalability}: the cost of sending data and
tasks to GPUs imposes a floor on task granularity relative to CPUs, reducing the advantage at small task granularities of
very lightweight mechanisms such as those in MPI.
